Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-13 paper/paper.tex
Title was incomplete
Format question
Abstract WIP

\title{Brief Announcement: An Improved Lower Bound for Dynamic Graph Partitioning}

@@

\keywords{online algorithms, competitive analysis, etc}

@@

\begin{abstract}
    Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\end{abstract}

@@

>>>>

\title{Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning}

@@

\keywords{online algorithms, competitive analysis}

@@

\begin{abstract}
  In the Dynamic Graph Partitioning problem, we are given a sequence of pairwise communication requests between n nodes, with patterns that may change over time.
  The objective is to service these requests by partitioning the nodes into $\ell$ clusters, each of size $k$, such that frequently communicating nodes are located in the same cluster.
  The partitioning can be updated dynamically by migrating nodes between clusters.
  The goal is to devise online algorithms which jointly minimize the amount of inter-cluster communication and migration cost.

\end{abstract}

@@

\todo{ACM format for review? With line numbers etc.}
